---
title: "Cohabiting_crangonyx_map"
author: "Marco Benucci"
date: "11 June 2019"
output: 
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Environment set-up

```{r environment setup, include=F}
## R(v3.5.1 - Win)
#.libPaths(c("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_win", .libPaths("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_win")))

## R(v3.5.1 - OSX)
#.libPaths(c("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_osx", .libPaths("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_osx")))

## R(v3.5.1 - ubuntu)
.libPaths(c("/home/mb/Dropbox/PhD Hull/PhD docs/Thesis/R_stats/rlib3.5_unix", .libPaths("/home/mb/Dropbox/PhD\ Hull/PhD\ docs/Thesis/R_stats/rlib3.5_unix")))
```

```{r directory, include=FALSE}
dir()
rm(list=ls())
ls()
```

Setting up the environment for R using the following packages.

```{r packages loading, include=F}
pack.list = c("broom","cowplot","devtools","dplyr","ggplot2","ggsn","gridExtra","leaflet","maps","maptools","mapview","raster","RColorBrewer","rgdal","rgeos","rworldmap","tmap")
new.packages = pack.list[!(pack.list %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, repos="https://cran.rstudio.com")
lapply(pack.list, require, character.only=T)
```

```{r session}
sessionInfo()
```

Plotting the map for Chapter 5 on DNA metabarcoding of trophic interactions of cohabiting _C. pseudogracilis_ and _C. floridanus_.

#1. Loading files 

Before mapping we load the files for the coordinates and the shapefiles.

```{r input data}
detect.sites = read.csv("map/Cf_detection_sites.csv")
ch.sites = read.csv("map/Chasewater_sites.csv")
```

Lakes coordinates include also a fourth lake which is part of this study, so it needs to be excluded from our current analysis.

```{r checking files plus removing one lake}
head(detect.sites)
head(ch.sites)
```

Adding the labels short name

```{r label}
detect.sites$Label = "NA"
detect.sites[grep("Thwaite", detect.sites$Description),"Label"] = "Thwai"
detect.sites[grep("Bourne", detect.sites$Description),"Label"] = "Bourn"
detect.sites[grep("Kyngs", detect.sites$Description),"Label"] = "Kyngs"
detect.sites[grep("Chasewater", detect.sites$Description),"Label"] = "Chase"
detect.sites[grep("Upton", detect.sites$Description),"Label"] = "Upton"
detect.sites[grep("Nar", detect.sites$Description),"Label"] = "Nar"
```

We load all shapefiles for the lakes and rivers sampled. If needed we can change the coordinates system to be in `WGS84` and then we create the map frame for plotting. In this case we leave all coordinates into British National Grid. The shapefiles are quite heavy to load individually, so we can load and transform them into one step saving a bit of memory.

In case we need to transform coordinates, the code below transforms the shapefiles coordinates into WGS84.
`wgs84='+proj=longlat +datum=WGS84'`
`map = fortify(spTransform(readOGR("shapefiles.shp"), CRS(wgs84)))`

All shapefiles were downloaded from:

`OS Open Map Local [Shape geospatial data], Scale 1:, Tile(s): TA, TF, TG, TL, SE, SK, SY, SZ, Updated: December 2017, Ordnance Survey, Using: EDINA Digimap Ordnance Survey Service, [http://digimap.edina.ac.uk/], Downloaded: July 2019`


```{r shapefiles}
# We load all the shapefiles and transform them to be read by ggplot.

# UK map
uk_map = fortify(readOGR("map/shapefiles/GB_IRworld.shp"))

# bourne stream
bo_map = fortify(readOGR("map/shapefiles/SZ_SurfaceWater_Area.shp"))
bo2_map = fortify(readOGR("map/shapefiles/SZ_Foreshore.shp"))
bo3_map = fortify(readOGR("map/shapefiles/SY_SurfaceWater_Area.shp"))
bo4_map = fortify(readOGR("map/shapefiles/SY_Foreshore.shp"))
bo5_map = fortify(readOGR("map/shapefiles/ST_SurfaceWater_Area.shp"))
bo6_map = fortify(readOGR("map/shapefiles/SU_SurfaceWater_Area.shp"))

# chasewater
ch_map = fortify(readOGR("map/shapefiles/SK_SurfaceWater_Area.shp"))

# kyngs dyke
ky_map = fortify(readOGR("map/shapefiles/TL_SurfaceWater_Area.shp"))

# river nar
na_map = fortify(readOGR("map/shapefiles/TF_SurfaceWater_Area.shp"))

# thwaite gardens
th_map = fortify(readOGR("map/shapefiles/TA_SurfaceWater_Area.shp"))
th2_map = fortify(readOGR("map/shapefiles/TA_Foreshore.shp"))
th3_map = fortify(readOGR("map/shapefiles/SE_SurfaceWater_Area.shp"))
th4_map = fortify(readOGR("map/shapefiles/SE_Foreshore.shp"))

# upton broad
up_map = fortify(readOGR("map/shapefiles/TG_SurfaceWater_Area.shp"))
up2_map = fortify(readOGR("map/shapefiles/TG_Foreshore.shp"))
```

#2. Mapping

We can now start plotting the sampling points and creates the maps, initially individually; then we plot them all together for publication.

```{r uk map}
png("map/UK_map.png", width=3000, height=3000, units="px", res=300)
ggplot(uk_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_rect(data=detect.sites[detect.sites$Label == "Bourn",], aes(xmin=390000, xmax=420000, ymin=80000, ymax=100000), color="red", fill="transparent") +
  geom_rect(data=detect.sites[detect.sites$Label == "Chase",], aes(xmin=400000, xmax=410000, ymin=300000, ymax=310000), color="red", fill="transparent") +
  geom_rect(data=detect.sites[detect.sites$Label == "Kyngs",], aes(xmin=500000, xmax=560000, ymin=270000, ymax=330000), color="red", fill="transparent") +
  geom_rect(data=detect.sites[detect.sites$Label == "Nar",], aes(xmin=560000, xmax=590000, ymin=300000, ymax=325000), color="red", fill="transparent") +
  geom_rect(data=detect.sites[detect.sites$Label == "Thwai",], aes(xmin=470000, xmax=540000, ymin=410000, ymax=450000), color="red", fill="transparent") +
  geom_rect(data=detect.sites[detect.sites$Label == "Upton",], aes(xmin=630000, xmax=660000, ymin=300000, ymax=320000), color="red", fill="transparent") +
  geom_text(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y, label="2"), nudge_y=-50000, cex=6) +
  geom_text(data=detect.sites[detect.sites$Label == "Chase",], aes(X,Y, label="1"), nudge_x=-30000, cex=6) +
  geom_text(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X,Y, label="3"), nudge_y=-60000, cex=6) +
  geom_text(data=detect.sites[detect.sites$Label == "Nar",], aes(X,Y, label="4"), nudge_x=10000, nudge_y=-40000, cex=6) +
  geom_text(data=detect.sites[detect.sites$Label == "Thwai",], aes(X,Y, label="5"), nudge_x=70000, cex=6) +
  geom_text(data=detect.sites[detect.sites$Label == "Upton",], aes(X,Y, label="6"), nudge_x=50000, cex=6) +
  coord_fixed(1) +
  theme_void() +
  north(uk_map, symbol=12, location="bottomleft")
dev.off()
```

```{r bourne map}
png("map/Bourne_map.png", width=3000, height=3000, units="px", res=300)
ggplot(bo_map) +
  geom_polygon(data=bo_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo3_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo4_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=4) +
  geom_label(data=detect.sites[detect.sites$Label == "Bourn",], aes(x=390000, y=108500, label="2."), cex=8) +
  coord_fixed(ratio=1, xlim=c(390000,420000), ylim=c(79000,108500)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0, r=0, b=0.25, l=0.25), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
  ggsn::scalebar(location="bottomleft", x.min=390000, x.max=400000, y.min=79000, y.max=85000, dist=5, dist_unit="km", st.dist=0.2, height=0.2, transform=F)
dev.off()
```

```{r chasewater map}
png("map/Chasewater_map.png", width=3000, height=3000, units="px", res=300)
ggplot(ch_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=ch.sites, aes(X, Y), color="red", cex=3) +
  geom_text(data=ch.sites, aes(X, Y, label=Title), nudge_x=25, nudge_y=-60, cex=4) +
  geom_label(data=detect.sites[detect.sites$Label == "Chase",], aes(X+100, Y, label=Description), cex=4) +
  geom_label(data=detect.sites[detect.sites$Label == "Chase",], aes(x=402500, y=309000, label="1."), cex=8) +
  coord_fixed(ratio=1, xlim=c(402500,404500), ylim=c(307000,309000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0, r=0.25, b=0.25, l=0.25), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
  ggsn::scalebar(location="bottomleft", x.min=402500, x.max=403600, y.min=307010, y.max=307020, dist=0.5, dist_unit="km", st.dist=5, height=5, transform=F)
dev.off()
```

```{r kyngs dyke map}
png("map/Kyngs_map.png", width=3000, height=3000, units="px", res=300)
ggplot(ky_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=na_map, aes(long,lat, group=group), fill="grey90", color="black") +
  geom_rect(aes(xmin=500000, xmax=525000, ymin=270000, ymax=272000), color="white", fill="white") +
  geom_point(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X, Y, label=Description), nudge_y=-3000, cex=4) +
  geom_label(data=detect.sites[detect.sites$Label == "Kyngs",], aes(x=500000, y=330000, label="3."), cex=8) +
  coord_fixed(ratio=1, xlim=c(500000,560000), ylim=c(270000,330000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0.25, r=0.25, b=0.25, l=0), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
  ggsn::scalebar(location="bottomleft", x.min=500000, x.max=510000, y.min=271000, y.max=272000, dist=12.5, dist_unit="km", st.dist=1, height=1, transform=F)
dev.off()
```

```{r nar river map}
png("map/Nar_map.png", width=3000, height=3000, units="px", res=300)
ggplot(na_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Nar",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Nar",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=4) +
  geom_label(data=detect.sites[detect.sites$Label == "Nar",], aes(x=560000, y=330000, label="4."), cex=8) +
  geom_rect(aes(xmin=559000, xmax=572000, ymin=299000, ymax=301500), color="white", fill="white") +
  coord_fixed(ratio=1, xlim=c(560000,590000), ylim=c(300000,330000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0.25, r=0.25, b=0.25, l=0.25), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
  ggsn::scalebar(location="bottomleft", x.min=560000, x.max=565000, y.min=300500, y.max=301000, dist=5, dist_unit="km", st.dist=2, height=2, transform=F)
dev.off()
```

```{r thwaite map}
png("map/Thwaite_map.png", width=3000, height=3000, units="px", res=300)
ggplot(th_map) +
  geom_polygon(data=th_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=th2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=th3_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=th4_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_rect(aes(xmin=470000, xmax=480000, ymin=406000, ymax=412000), fill="white", color="white") +
  geom_point(data=detect.sites[detect.sites$Label == "Thwai",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Thwai",], aes(X, Y, label=Description), nudge_y=-3000, cex=4) +
  geom_label(data=detect.sites[detect.sites$Label == "Thwai",], aes(x=469000,y=475000, label="5."), cex=8) +
  coord_fixed(ratio=1, xlim=c(469000,541000), ylim=c(405000,475000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0.25, r=0, b=0.25, l=0.25), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
  ggsn::scalebar(location="bottomleft", x.min=470000, x.max=479000, y.min=406000, y.max=410000, dist=10, dist_unit="km", st.dist=0.4, height=0.5, transform=F)
dev.off()
```

```{r upton map}
png("map/Upton_map.png", width=3000, height=3000, units="px", res=300)
ggplot(up_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=up2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_rect(aes(xmin=629000, xmax=635000, ymin=290000, ymax=301000), color="white", fill="white") +
  geom_point(data=detect.sites[detect.sites$Label == "Upton",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Upton",], aes(X, Y, label=Description), nudge_x=0, nudge_y=1000, cex=4) +
  coord_fixed(ratio=1, xlim=c(630000,660000), ylim=c(300000,320000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=630000, x.max=631000, y.min=300000, y.max=300100, dist=3000, dist_unit="m", st.dist=5, height=4, transform=F)
dev.off()
```

#3. Complete map for publication.

Complete map for publication

```{r complete map}
uk = ggplot(uk_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_rect(data=detect.sites[detect.sites$Label == "Bourn",], aes(xmin=390000, xmax=420000, ymin=79000, ymax=108500), color="black", fill="transparent", cex=1) +
  geom_rect(data=detect.sites[detect.sites$Label == "Chase",], aes(xmin=402500, xmax=404500, ymin=307000, ymax=309000), color="black", fill="transparent", cex=1) +
  geom_rect(data=detect.sites[detect.sites$Label == "Kyngs",], aes(xmin=500000, xmax=560000, ymin=270000, ymax=330000), color="black", fill="transparent", cex=1) + 
  geom_rect(data=detect.sites[detect.sites$Label == "Nar",], aes(xmin=560000, xmax=590000, ymin=300000, ymax=330000), color="black", fill="transparent", cex=1) +
  geom_rect(data=detect.sites[detect.sites$Label == "Thwai",], aes(xmin=469000, xmax=541000, ymin=405000, ymax=475000), color="black", fill="transparent", cex=1) +
  geom_rect(data=detect.sites[detect.sites$Label == "Upton",], aes(xmin=630000, xmax=659000, ymin=301000, ymax=329000), color="black", fill="transparent", cex=1) +
  geom_text(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y, label="5"), nudge_y=-50000, cex=7) +
  geom_text(data=detect.sites[detect.sites$Label == "Chase",], aes(X,Y, label="1"), nudge_x=-30000, cex=7) +
  geom_text(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X,Y, label="4"), nudge_y=-70000, cex=7) +
  geom_text(data=detect.sites[detect.sites$Label == "Nar",], aes(X,Y, label="3"), nudge_x=10000, nudge_y=-50000, cex=7) +
  geom_text(data=detect.sites[detect.sites$Label == "Thwai",], aes(X,Y, label="2"), nudge_x=70000, cex=7) +
  geom_text(data=detect.sites[detect.sites$Label == "Upton",], aes(X,Y, label="6"), nudge_x=50000, cex=7) +
  coord_fixed(1) +
  theme_void() +
  theme(plot.margin=unit(c(t=0, r=0.25, b=0.25, l=0), unit="cm")) +
  north(uk_map, symbol=12, location="bottomleft")

bo = ggplot(bo_map) +
  geom_polygon(data=bo_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo3_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo4_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo5_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo6_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y), shape=24, fill="red", color="red", cex=4) +
#  geom_label(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=4) +
  geom_label(data=detect.sites[detect.sites$Label == "Bourn",], aes(x=390400, y=108250, label="5."), cex=10) +
  coord_fixed(ratio=1, xlim=c(390000,420000), ylim=c(79000,108500)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0, r=0, b=0.25, l=0.25), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
  ggsn::scalebar(location="bottomleft", x.min=390000, x.max=400000, y.min=80000, y.max=85000, dist=5, dist_unit="km", st.dist=0.2, height=0.2, transform=F)

ch = ggplot(ch_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=ch.sites, aes(X, Y), color="red", cex=4) +
  geom_text(data=ch.sites, aes(X, Y, label=Title), nudge_x=25, nudge_y=-70, cex=4) +
#  geom_label(data=detect.sites[detect.sites$Label == "Chase",], aes(X+100, Y, label=Description), cex=4) +
  geom_label(data=detect.sites[detect.sites$Label == "Chase",], aes(x=402520, y=308985, label="1."), cex=10) +
  coord_fixed(ratio=1, xlim=c(402500,404500), ylim=c(307000,309000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0, r=0.25, b=0.25, l=0.25), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
  ggsn::scalebar(location="bottomleft", x.min=402500, x.max=403600, y.min=307050, y.max=307070, dist=0.5, dist_unit="km", st.dist=3, height=3, transform=F)

ky = ggplot(ky_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=na_map, aes(long,lat, group=group), fill="grey90", color="black") +
  geom_rect(aes(xmin=500000, xmax=527500, ymin=267000, ymax=274000), color="white", fill="white") +
  geom_point(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X, Y), shape=22 ,color="red", fill="red", cex=4) +
#  geom_label(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X, Y, label=Description), nudge_y=-3000, cex=4) +
  geom_label(data=detect.sites[detect.sites$Label == "Kyngs",], aes(x=500800, y=329500, label="4."), cex=10) +
  coord_fixed(ratio=1, xlim=c(500000,560000), ylim=c(270000,330000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0.25, r=0.25, b=0.25, l=0), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
  ggsn::scalebar(location="bottomleft", x.min=500000, x.max=510000, y.min=271000, y.max=272000, dist=12.5, dist_unit="km", st.dist=2, height=2, transform=F)

na = ggplot(na_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Nar",], aes(X, Y), shape=24, fill="red", color="red", cex=4) +
#  geom_label(data=detect.sites[detect.sites$Label == "Nar",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=4) +
  geom_label(data=detect.sites[detect.sites$Label == "Nar",], aes(x=560400, y=329800, label="3."), cex=10) +
  geom_rect(aes(xmin=555500, xmax=572000, ymin=299000, ymax=301800), color="white", fill="white") +
  coord_fixed(ratio=1, xlim=c(560000,590000), ylim=c(300000,330000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0.25, r=0.25, b=0.25, l=0.25), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
  ggsn::scalebar(location="bottomleft", x.min=560000, x.max=565000, y.min=300500, y.max=301000, dist=5, dist_unit="km", st.dist=2, height=2, transform=F)

th = ggplot(th_map) +
  geom_polygon(data=th_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=th2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=th3_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=th4_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_rect(aes(xmin=460000, xmax=499700, ymin=402000, ymax=408500), fill="white", color="white") +
  geom_point(data=detect.sites[detect.sites$Label == "Thwai",], aes(X, Y), shape=24, fill="red", color="red", cex=4) +
#  geom_label(data=detect.sites[detect.sites$Label == "Thwai",], aes(X, Y, label=Description), nudge_y=-3000, cex=4) +
  geom_label(data=detect.sites[detect.sites$Label == "Thwai",], aes(x=469700,y=474400, label="2."), cex=10) +
  coord_fixed(ratio=1, xlim=c(469000,542000), ylim=c(405000,475000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0.25, r=0, b=0.25, l=0.25), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
  ggsn::scalebar(location="bottomleft", x.min=470000, x.max=479000, y.min=406000, y.max=410000, dist=12.5, dist_unit="km", st.dist=0.4, height=0.5, transform=F)

up = ggplot(up_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=up2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_rect(aes(xmin=628000, xmax=641500, ymin=298000, ymax=302800), color="white", fill="white") +
  geom_point(data=detect.sites[detect.sites$Label == "Upton",], aes(X, Y), shape=24, fill="red", color="red", cex=4) +
#  geom_label(data=detect.sites[detect.sites$Label == "Upton",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=4) +
  geom_label(data=detect.sites[detect.sites$Label == "Upton",], aes(x=629700, y=328750, label="6."), cex=10) +
  coord_fixed(ratio=1, xlim=c(629500,659000), ylim=c(301000,329000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0.25, r=0, b=0, l=0), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
  ggsn::scalebar(location="bottomleft", x.min=629500, x.max=631000, y.min=302000, y.max=303100, dist=5, dist_unit="km", st.dist=1, height=0.7, transform=F)

png("map/sampling_map.png", width=4000, height=4000, units="px", res=300)
plot_grid(uk, ch, th, na, ky, na, bo, up, ncol=3, nrow=3)
dev.off()
```

```{r log session info}
sink("log_session_map-creation.txt")
sessionInfo()
citation()
sink()
```

```{r packages citation}
sink("map-creation_packages_citations.txt")
for (p in pack.list){
 print(citation(p))
}
sink()
```

```{r end}
print("end")
```