---
title: "Cohabiting_crangonyx_map"
author: "Marco Benucci"
date: "11 June 2019"
output: 
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Environment set-up

```{r environment setup, include=F}
## R(v3.5.1 - Win)
#.libPaths(c("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_win", .libPaths("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_win")))

## R(v3.5.1 - OSX)
#.libPaths(c("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_osx", .libPaths("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_osx")))

## R(v3.5.1 - ubuntu)
.libPaths(c("/home/mb/Dropbox/PhD Hull/PhD docs/Thesis/R_stats/rlib3.5_unix", .libPaths("/home/mb/Dropbox/PhD\ Hull/PhD\ docs/Thesis/R_stats/rlib3.5_unix")))
```

```{r directory, include=FALSE}
dir()
rm(list=ls())
ls()
```

Setting up the environment for R using the following packages.

```{r packages loading, include=F}
pack.list = c("broom","cowplot","devtools","dplyr","ggplot2","ggsn","gridExtra","leaflet","maps","maptools","mapview","raster","RColorBrewer","rgdal","rgeos","rworldmap","tmap")
new.packages = pack.list[!(pack.list %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, repos="https://cran.rstudio.com")
lapply(pack.list, require, character.only=T)
```

```{r session}
sessionInfo()
```

## Plotting the map for Chapter 5 on DNA metabarcoding of trophic interactions of cohabiting _C. pseudogracilis_ and _C. floridanus_.

```{r input data}
detect.sites = read.csv("map/Cf_detection_sites.csv")
ch.sites = read.csv("map/Chasewater_sites.csv")
#lake.coords = read.csv("map/site_coords.csv")
```

Lakes coordinates include also a fourth lake which is part of this study, so it needs to be excluded from our current analysis.

```{r checking files plus removing one lake}
head(detect.sites)
head(ch.sites)
#head(lake.coords)
```

Adding the labels short name

```{r label}
detect.sites$Label = "NA"
detect.sites[grep("Thwaite", detect.sites$Description),"Label"] = "Thwai"
detect.sites[grep("Bourne", detect.sites$Description),"Label"] = "Bourn"
detect.sites[grep("Kyngs", detect.sites$Description),"Label"] = "Kyngs"
detect.sites[grep("Chasewater", detect.sites$Description),"Label"] = "Chase"
detect.sites[grep("Upton", detect.sites$Description),"Label"] = "Upton"
detect.sites[grep("Nar", detect.sites$Description),"Label"] = "Nar"
```

We load all shapefiles for the lakes and rivers sampled. We change the coorinates system to be in `WGS84` and then we create the map frame for plotting.

All shapefiles were downloaded from:

`OS Open Map Local [Shape geospatial data], Scale 1:, Tile(s): TA, TF, TG, TL, SK, SZ, Updated: December 2017, Ordnance Survey, Using: EDINA Digimap Ordnance Survey Service, [http://digimap.edina.ac.uk/], Downloaded: July 2019`


```{r shapefiles}
uk_shape = readOGR("map/shapefiles/GB_IRworld.shp")

bourne_areashape = readOGR("map/shapefiles/SZ_SurfaceWater_Area.shp")
bourne_coastshape = readOGR("map/shapefiles/SZ_Foreshore.shp")
bourne_areashape2 = readOGR("map/shapefiles/SY_SurfaceWater_Area.shp")
bourne_coastshape2 = readOGR("map/shapefiles/SY_Foreshore.shp")

chase_areashape = readOGR("map/shapefiles/SK_SurfaceWater_Area.shp")

kyngs_areashape = readOGR("map/shapefiles/TL_SurfaceWater_Area.shp")
#kyngs_lineshape

nar_areashape = readOGR("map/shapefiles/TF_SurfaceWater_Area.shp")

thwaite_areashape = readOGR("map/shapefiles/TA_SurfaceWater_Area.shp")
thwaite_coastshape = readOGR("map/shapefiles/TA_Foreshore.shp")
thwaite_areashape2 = readOGR("map/shapefiles/SE_SurfaceWater_Area.shp")

upton_areashape = readOGR("map/shapefiles/TG_SurfaceWater_Area.shp")

# Because we have coordinates in National Grid, we convert into WGS84
#wgs84 = '+proj=longlat +datum=WGS84'

#uk overview
uk_map = fortify(uk_shape)

#bourne stream
bo_map = fortify(bourne_areashape)
bo2_map = fortify(bourne_coastshape)
bo3_map = fortify(bourne_areashape2)
bo4_map = fortify(bourne_coastshape2)

#chasewater reservoir
ch_map = fortify(chase_areashape)

#kyngs dyke
ky_map = fortify(kyngs_areashape)

#nar river
na_map = fortify(nar_areashape)

#thwaite gardens
th_map = fortify(thwaite_areashape)
th2_map = fortify(thwaite_coastshape)
th3_map = fortify(thwaite_areashape2)

#upton broad
up_map = fortify(upton_areashape)
```

We can now start plotting the sampling points and creates the maps, initially individually; then we plot them all together for publication.

```{r uk map}
png("map/UK_map.png", width=3000, height=3000, units="px", res=300)
ggplot(uk_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_point(data=detect.sites, aes(X,Y), color="black", cex=3) +
  geom_text(data=detect.sites, aes(X,Y, label=Label), nudge_y=-20000, cex=4) +
  coord_fixed(1) +
  theme_void() +
  north(uk_map, symbol=12, location="bottomleft")
dev.off()
```

```{r chasewater map}
png("map/Chasewater_map.png", width=3000, height=3000, units="px", res=300)
ggplot(ch_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=ch.sites, aes(X, Y), color="red", cex=3) +
  geom_label(data=ch.sites, aes(X, Y, label=Title), nudge_x=150, nudge_y=0, cex=4) +
  coord_fixed(ratio=1, xlim=c(402500,404100), ylim=c(307000,308900)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=402500, x.max=404100, y.min=307000, y.max=307050, dist=300, dist_unit="m", st.dist=1, height=1, transform=F)
dev.off()
```

```{r bourne map}
png("map/Bourne_map.png", width=3000, height=3000, units="px", res=300)
ggplot(bo_map) +
  geom_polygon(data=bo_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo3_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo4_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=4) +
  coord_fixed(ratio=1, xlim=c(390000,420000), ylim=c(80000,100000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=390000, x.max=400000, y.min=81000, y.max=85000, dist=5000, dist_unit="m", st.dist=0.2, height=0.2, transform=F)
dev.off()
```

```{r kyngs dyke map}
png("map/Kyngs_map.png", width=3000, height=3000, units="px", res=300)
ggplot(ky_map) +
  geom_polygon(data=ky_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=na_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X, Y, label=Description), nudge_x=0, nudge_y=-3000, cex=4) +
  geom_rect(aes(xmin=490000, xmax=535000, ymin=277500, ymax=283000),color="white",fill="white") +
  coord_fixed(ratio=1, xlim=c(500000,560000), ylim=c(280000,340000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=500000, x.max=510000, y.min=281000, y.max=290000, dist=15000, dist_unit="m", st.dist=0.25, height=0.2, transform=F)
dev.off()
```

```{r nar river map}
png("map/Nar_map.png", width=3000, height=3000, units="px", res=300)
ggplot(na_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Nar",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Nar",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=4) +
  coord_fixed(ratio=1, xlim=c(560000,590000), ylim=c(300000,325000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=560000, x.max=565000, y.min=300100, y.max=301000, dist=5000, dist_unit="m", st.dist=1, height=1, transform=F)
dev.off()
```

```{r thwaite map}
png("map/Thwaite_map.png", width=3000, height=3000, units="px", res=300)
ggplot(th_map) +
  geom_polygon(data=th_map, aes(long,lat,group = group), fill="gray90", color="gray10") +
  geom_polygon(data=th2_map, aes(long,lat,group = group), fill="gray90", color="gray10") +
  geom_polygon(data=th3_map, aes(long,lat,group = group), fill="gray90", color="gray10") +
  geom_point(data=detect.sites[detect.sites$Label == "Thwai",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Thwai",], aes(X, Y, label=Description), nudge_y=-3000, cex=4) +
  coord_fixed(ratio=1, xlim=c(480000,540000), ylim=c(400000,450000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=480000, x.max=540000, y.min=400000, y.max=401000, dist=10000, dist_unit="m", st.dist=1.5, height=1, transform=F)
dev.off()
```

```{r upton map}
png("map/Upton_map.png", width=3000, height=3000, units="px", res=300)
ggplot(up_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Upton",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Upton",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=4) +
  coord_fixed(ratio=1, xlim=c(630000,650000), ylim=c(310000,320000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=630000, x.max=631000, y.min=310000, y.max=310100, dist=2500, dist_unit="m", st.dist=3, height=3, transform=F)
dev.off()
```

Complete map for publication

```{r complete map}
uk = ggplot(uk_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_point(data=detect.sites, aes(X,Y), color="black", cex=3) +
  geom_text(data=detect.sites, aes(X,Y, label=Label), nudge_y=-20000, cex=4) +
  coord_fixed(1) +
  theme_void() +
  north(uk_map, symbol=12, location="bottomleft")

ch = ggplot(ch_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=ch.sites, aes(X, Y), color="red", cex=3) +
  geom_label(data=ch.sites, aes(X, Y, label=Title), nudge_x=150, nudge_y=0, cex=4) +
  coord_fixed(ratio=1, xlim=c(402500,404100), ylim=c(307000,308900)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=402500, x.max=404100, y.min=307000, y.max=307050, dist=300, dist_unit="m", st.dist=1, height=1, transform=F)

bo = ggplot(bo_map) +
  geom_polygon(data=bo_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo3_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo4_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=4) +
  coord_fixed(ratio=1, xlim=c(390000,420000), ylim=c(80000,100000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=390000, x.max=400000, y.min=81000, y.max=85000, dist=5000, dist_unit="m", st.dist=0.2, height=0.2, transform=F)

ky = ggplot(ky_map) +
  geom_polygon(data=ky_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=na_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X, Y, label=Description), nudge_x=0, nudge_y=-3000, cex=4) +
  geom_rect(aes(xmin=490000, xmax=535000, ymin=277500, ymax=283000),color="white",fill="white") +
  coord_fixed(ratio=1, xlim=c(500000,560000), ylim=c(280000,340000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=500000, x.max=510000, y.min=281000, y.max=290000, dist=15000, dist_unit="m", st.dist=0.25, height=0.2, transform=F)

na = ggplot(na_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Nar",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Nar",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=4) +
  coord_fixed(ratio=1, xlim=c(560000,590000), ylim=c(300000,325000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=560000, x.max=565000, y.min=300100, y.max=301000, dist=5000, dist_unit="m", st.dist=1, height=1, transform=F)

th = ggplot(th_map) +
  geom_polygon(data=th_map, aes(long,lat,group = group), fill="gray90", color="gray10") +
  geom_polygon(data=th2_map, aes(long,lat,group = group), fill="gray90", color="gray10") +
  geom_polygon(data=th3_map, aes(long,lat,group = group), fill="gray90", color="gray10") +
  geom_point(data=detect.sites[detect.sites$Label == "Thwai",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Thwai",], aes(X, Y, label=Description), nudge_y=-3000, cex=4) +
  coord_fixed(ratio=1, xlim=c(480000,540000), ylim=c(400000,450000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=480000, x.max=540000, y.min=400000, y.max=401000, dist=10000, dist_unit="m", st.dist=1.5, height=1, transform=F)

up = ggplot(up_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Upton",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Upton",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=4) +
  coord_fixed(ratio=1, xlim=c(630000,650000), ylim=c(310000,320000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=630000, x.max=631000, y.min=310000, y.max=310100, dist=2500, dist_unit="m", st.dist=3, height=3, transform=F) 

png("map/sampling_map.png", width=9000, height=9000, units="px", res=350)
plot_grid(uk, ch, bo, ky, na, th, up, ncol=3, nrow=2)
dev.off()
```

```{r log session info}
sink("log_session_map-creation.txt")
sessionInfo()
citation()
sink()
```

```{r packages citation}
sink("map-creation_packages_citations.txt")
for (p in pack.list){
 print(citation(p))
}
sink()
```

```{r}
print("end")
```