---
title: "Cohabiting_crangonyx_map"
author: "Marco Benucci"
date: "11 June 2019"
output: 
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Environment set-up

```{r environment setup, include=F}
## R(v3.5.1 - Win)
#.libPaths(c("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_win", .libPaths("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_win")))

## R(v3.5.1 - OSX)
#.libPaths(c("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_osx", .libPaths("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_osx")))

## R(v3.5.1 - ubuntu)
.libPaths(c("/home/mb/Dropbox/PhD Hull/PhD docs/Thesis/R_stats/rlib3.5_unix", .libPaths("/home/mb/Dropbox/PhD\ Hull/PhD\ docs/Thesis/R_stats/rlib3.5_unix")))
```

```{r directory, include=FALSE}
dir()
rm(list=ls())
ls()
```

Setting up the environment for R using the following packages.

```{r packages loading, include=F}
pack.list = c("broom","cowplot","devtools","dplyr","ggplot2","ggsn","gridExtra","leaflet","maps","maptools","mapview","raster","RColorBrewer","rgdal","rgeos","rworldmap","tmap")
new.packages = pack.list[!(pack.list %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, repos="https://cran.rstudio.com")
lapply(pack.list, require, character.only=T)
```

```{r session}
sessionInfo()
```

## Plotting the map for Chapter 3 on DNA metabarcoding and MATI of invasive _D. villosus_ against non-invasive _G. zaddachi_.

```{r input data}
ch.sites = read.csv("map/Chasewater_sites.csv")
lake.coords = read.csv("map/site_coords.csv")
```

Lakes coordinates include also a fourth lake which is part of this study, so it needs to be excluded from our current analysis.

```{r checking files plus removing one lake}
head(ch.sites)
head(lake.coords)
```

Adding the labels short name

```{r label}
lake.coords$short.name = "CH"
```

```{r shapefiles}
uk_shape = readOGR("map/shapefiles/GB_IRworld.shp")

# Because we have coordinates in National Grid, we convert into WGS84
wgs84 = '+proj=longlat +datum=WGS84'
uk_shape_wgs = spTransform(uk_shape, CRS(wgs84))
uk_map = fortify(uk_shape_wgs)

chasewater_shape = readOGR("map/shapefiles/SK_SurfaceWater_Area.shp")
ch.sites
# Because we have coordinates in National Grid, we convert into WGS84
chasewater_wgs = spTransform(chasewater_shape, CRS(wgs84))
ch_map = fortify(chasewater_wgs)
```

```{r uk map}
png("map/UK_map.png", width=3000, height=3000, units="px", res=300)
ggplot(uk_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_point(data=lake.coords, aes(Longitude,Latitude), color="black", cex=3) +
  geom_text(data=lake.coords, aes(Longitude,Latitude, label=ID), nudge_x=0.6, nudge_y=-0.2, cex=4) +
  coord_fixed(2) +
  theme_void() +
  north(uk_map, symbol=12, location="bottomleft")
dev.off()
```

Importing the lakes shapefiles to plot the sampling points

```{r chasewater map}
png("map/Chasewater_map.png", width=3000, height=3000, units="px", res=300)
ggplot(ch_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=ch.sites, aes(Longitude, Latitude), color="red", cex=3) +
  geom_text(data=ch.sites, aes(Longitude, Latitude, label=Title), nudge_x=0.0007, nudge_y=-0.0001, cex=4) +
  xlim(-1.963,-1.937) + ylim(52.660,52.679) +
  coord_fixed(1.5) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=-1.962, x.max=-1.958, y.min=52.6625, y.max=52.665, dist=300, dist_unit="m", st.dist=0.2, height=0.15, transform=T)
dev.off()
```
```{r complete map}
png("map/sampling_map.png", width=6000, height=6000, units="px", res=300)
a = ggplot(uk_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_point(data=lake.coords, aes(Longitude,Latitude), color="black", cex=6) +
  geom_text(data=lake.coords, aes(Longitude,Latitude, label=ID), nudge_x=0.6, nudge_y=-0.2, cex=7) +
  coord_fixed(2) +
  theme_void() +
  north(uk_map, symbol=12, location="bottomleft") +
  theme(plot.margin=unit(c(0,0.25,0,0.25), "cm"))

b = ggplot(ch_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=ch.sites, aes(Longitude, Latitude), color="red", cex=6) +
  geom_text(data=ch.sites, aes(Longitude, Latitude, label=Title), nudge_x=0.0015, nudge_y=-0.0001, cex=7) +
  xlim(-1.963,-1.937) + ylim(52.660,52.679) +
  coord_fixed(1.5) +
  theme_void() +
    blank() +
  ggsn::scalebar(location="bottomleft", x.min=-1.962, x.max=-1.958, y.min=52.6625, y.max=52.665, dist=300, dist_unit="m", st.dist=0.2, height=0.15, transform=T)
  

plot_grid(a,b, ncol=2)
dev.off()
```

```{r log session info}
sink("log_session_map-creation.txt")
sessionInfo()
citation()
sink()
```

```{r packages citation}
sink("map-creation_packages_citations.txt")
for (p in pack.list){
 print(citation(p))
}
sink()
```

```{r}
print("end")
```