---
title: "Cohabiting_crangonyx_map"
author: "Marco Benucci"
date: "11 June 2019"
output: 
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Environment set-up

```{r environment setup, include=F}
## R(v3.5.1 - Win)
#.libPaths(c("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_win", .libPaths("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_win")))

## R(v3.5.1 - OSX)
#.libPaths(c("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_osx", .libPaths("D:\\Dropbox\\PhD Hull\\PhD docs\\Thesis\\R_stats\\rlib3.5_osx")))

## R(v3.5.1 - ubuntu)
.libPaths(c("/home/mb/Dropbox/PhD Hull/PhD docs/Thesis/R_stats/rlib3.5_unix", .libPaths("/home/mb/Dropbox/PhD\ Hull/PhD\ docs/Thesis/R_stats/rlib3.5_unix")))
```

```{r directory, include=FALSE}
dir()
rm(list=ls())
ls()
```

Setting up the environment for R using the following packages.

```{r packages loading, include=F}
pack.list = c("broom","cowplot","devtools","dplyr","ggplot2","ggsn","gridExtra","leaflet","maps","maptools","mapview","raster","RColorBrewer","rgdal","rgeos","rworldmap","tmap")
new.packages = pack.list[!(pack.list %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, repos="https://cran.rstudio.com")
lapply(pack.list, require, character.only=T)
```

```{r session}
sessionInfo()
```

## Plotting the map for Chapter 5 on DNA metabarcoding of trophic interactions of cohabiting _C. pseudogracilis_ and _C. floridanus_.

```{r input data}
detect.sites = read.csv("map/Cf_detection_sites.csv")
ch.sites = read.csv("map/Chasewater_sites.csv")
```

Lakes coordinates include also a fourth lake which is part of this study, so it needs to be excluded from our current analysis.

```{r checking files plus removing one lake}
head(detect.sites)
head(ch.sites)
```

Adding the labels short name

```{r label}
detect.sites$Label = "NA"
detect.sites[grep("Thwaite", detect.sites$Description),"Label"] = "Thwai"
detect.sites[grep("Bourne", detect.sites$Description),"Label"] = "Bourn"
detect.sites[grep("Kyngs", detect.sites$Description),"Label"] = "Kyngs"
detect.sites[grep("Chasewater", detect.sites$Description),"Label"] = "Chase"
detect.sites[grep("Upton", detect.sites$Description),"Label"] = "Upton"
detect.sites[grep("Nar", detect.sites$Description),"Label"] = "Nar"
```

We load all shapefiles for the lakes and rivers sampled. We change the coorinates system to be in `WGS84` and then we create the map frame for plotting.

All shapefiles were downloaded from:

`OS Open Map Local [Shape geospatial data], Scale 1:, Tile(s): TA, TF, TG, TL, SE, SK, SZ, Updated: December 2017, Ordnance Survey, Using: EDINA Digimap Ordnance Survey Service, [http://digimap.edina.ac.uk/], Downloaded: July 2019`


```{r shapefiles}
# We load all the shapefiles

uk_shape = readOGR("map/shapefiles/GB_IRworld.shp")
bourne_shape = readOGR("map/shapefiles/SZ_SurfaceWater_Area.shp")
bourne2_shape = readOGR("map/shapefiles/SZ_Foreshore.shp")
chasewater_shape = readOGR("map/shapefiles/SK_SurfaceWater_Area.shp")
kyngs_shape = readOGR("map/shapefiles/TL_SurfaceWater_Area.shp")
nar_shape = readOGR("map/shapefiles/TF_SurfaceWater_Area.shp")
thwaite_shape = readOGR("map/shapefiles/TA_SurfaceWater_Area.shp")
thwaite2_shape = readOGR("map/shapefiles/TA_Foreshore.shp")
thwaite3_shape = readOGR("map/shapefiles/SE_SurfaceWater_Area.shp")
upton_shape = readOGR("map/shapefiles/TG_SurfaceWater_Area.shp")
upton2_shape = readOGR("map/shapefiles/TG_Foreshore.shp")

# In case we need to transform coordinates from British National Grid into WGS84
# wgs84='+proj=longlat +datum=WGS84'
# uk_shape_wgs = spTransform(uk_shape, CRS(wgs84))

# UK map
uk_map = fortify(uk_shape)

# chasewater
ch_map = fortify(chasewater_shape)

# bourne stream
bo_map = fortify(bourne_shape)
bo2_map = fortify(bourne2_shape)

# kyngs dyke
ky_map = fortify(kyngs_shape)

# river nar
na_map = fortify(nar_shape)

# thwaite gardens
th_map = fortify(thwaite_shape)
th2_map = fortify(thwaite2_shape)
th3_map = fortify(thwaite3_shape)

# upton broad
up_map = fortify(upton_shape)
up2_map = fortify(upton2_shape)
```


We can now start plotting the sampling points and creates the maps, initially individually; then we plot them all together for publication.

```{r uk map}
png("map/UK_map.png", width=3000, height=3000, units="px", res=300)
ggplot(uk_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_rect(data=detect.sites[detect.sites$Label == "Bourn",], aes(xmin=390000, xmax=420000, ymin=80000, ymax=100000), color="red", fill="transparent") +
  geom_rect(data=detect.sites[detect.sites$Label == "Chase",], aes(xmin=400000, xmax=410000, ymin=300000, ymax=310000), color="red", fill="transparent") +
  geom_rect(data=detect.sites[detect.sites$Label == "Kyngs",], aes(xmin=500000, xmax=560000, ymin=270000, ymax=330000), color="red", fill="transparent") +
  geom_rect(data=detect.sites[detect.sites$Label == "Nar",], aes(xmin=560000, xmax=590000, ymin=300000, ymax=325000), color="red", fill="transparent") +
  geom_rect(data=detect.sites[detect.sites$Label == "Thwai",], aes(xmin=470000, xmax=540000, ymin=410000, ymax=450000), color="red", fill="transparent") +
  geom_rect(data=detect.sites[detect.sites$Label == "Upton",], aes(xmin=630000, xmax=660000, ymin=300000, ymax=320000), color="red", fill="transparent") +
  geom_text(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y, label="2"), nudge_y=-50000, cex=6) +
  geom_text(data=detect.sites[detect.sites$Label == "Chase",], aes(X,Y, label="1"), nudge_x=-30000, cex=6) +
  geom_text(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X,Y, label="3"), nudge_y=-60000, cex=6) +
  geom_text(data=detect.sites[detect.sites$Label == "Nar",], aes(X,Y, label="4"), nudge_x=10000, nudge_y=-40000, cex=6) +
  geom_text(data=detect.sites[detect.sites$Label == "Thwai",], aes(X,Y, label="5"), nudge_x=70000, cex=6) +
  geom_text(data=detect.sites[detect.sites$Label == "Upton",], aes(X,Y, label="6"), nudge_x=50000, cex=6) +
  coord_fixed(1) +
  theme_void() +
  north(uk_map, symbol=12, location="bottomleft")
dev.off()
```

```{r}
png("map/Bourne_map.png", width=3000, height=3000, units="px", res=300)
ggplot(bo_map) +
  geom_polygon(data=bo_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y, label=Description), nudge_x=0, nudge_y=1000, cex=4) +
  coord_fixed(ratio=1, xlim=c(390000,420000), ylim=c(80000,100000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=390000, x.max=400000, y.min=81000, y.max=85000, dist=5000, dist_unit="m", st.dist=0.2, height=0.2, transform=F)
dev.off()
```



```{r chasewater map}
png("map/Chasewater_map.png", width=3000, height=3000, units="px", res=300)
ggplot(ch_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=ch.sites, aes(X, Y), color="red", cex=3) +
  geom_text(data=ch.sites, aes(X, Y, label=Title), nudge_x=25, nudge_y=-60, cex=4) +
  coord_fixed(ratio=1, xlim=c(402500,404100), ylim=c(307000,308900)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=402500, x.max=403600, y.min=307010, y.max=307020, dist=300, dist_unit="m", st.dist=5, height=5, transform=F)
dev.off()
```

```{r}
png("map/Kyngs_map.png", width=3000, height=3000, units="px", res=300)
ggplot(ky_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=na_map, aes(long,lat, group=group), fill="grey90", color="black") +
  geom_rect(aes(xmin=500000, xmax=525000, ymin=267000, ymax=273000), color="white", fill="white") +
  geom_point(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X, Y, label=Description), nudge_y=-3000, cex=4) +
  coord_fixed(ratio=1, xlim=c(500000,560000), ylim=c(270000,330000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=500000, x.max=510000, y.min=270000, y.max=271000, dist=10000, dist_unit="m", st.dist=2, height=1, transform=F)
dev.off()
```

```{r nar river map}
png("map/Nar_map.png", width=3000, height=3000, units="px", res=300)
ggplot(na_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Nar",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Nar",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=4) +
  geom_rect(aes(xmin=559500, xmax=572200, ymin=299000, ymax=301500), color="white", fill="white") +
  coord_fixed(ratio=1, xlim=c(560000,590000), ylim=c(300000,325000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=560000, x.max=565000, y.min=300100, y.max=301000, dist=5000, dist_unit="m", st.dist=1, height=1, transform=F)
dev.off()
```


```{r thwaite map}
png("map/Thwaite_map.png", width=3000, height=3000, units="px", res=300)
ggplot(th_map) +
  geom_polygon(data=th_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=th2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=th3_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_rect(aes(xmin=470000, xmax=495000, ymin=405000, ymax=412000), fill="white", color="white") +
  geom_point(data=detect.sites[detect.sites$Label == "Thwai",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Thwai",], aes(X, Y, label=Description), nudge_y=-2500, cex=4) +
  coord_fixed(ratio=1, xlim=c(470000,540000), ylim=c(410000,450000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=471000, x.max=480000, y.min=410000, y.max=415000, dist=10000, dist_unit="m", st.dist=0.2, height=0.3, transform=F)
dev.off()
```


```{r upton map}
png("map/Upton_map.png", width=3000, height=3000, units="px", res=300)
ggplot(up_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=up2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_rect(aes(xmin=629000, xmax=635000, ymin=290000, ymax=301000), color="white", fill="white") +
  geom_point(data=detect.sites[detect.sites$Label == "Upton",], aes(X, Y), color="red", cex=3) +
  geom_label(data=detect.sites[detect.sites$Label == "Upton",], aes(X, Y, label=Description), nudge_x=0, nudge_y=1000, cex=4) +
  coord_fixed(ratio=1, xlim=c(630000,660000), ylim=c(300000,320000)) +
  theme_void() +
  blank() +
  ggsn::scalebar(location="bottomleft", x.min=630000, x.max=631000, y.min=300000, y.max=300100, dist=3000, dist_unit="m", st.dist=5, height=4, transform=F)
dev.off()
```

Complete map for publication

```{r complete map}
uk = ggplot(uk_map) +
  geom_polygon(aes(long,lat,group = group), fill="white", color="black") +
  geom_rect(data=detect.sites[detect.sites$Label == "Bourn",], aes(xmin=390000, xmax=420000, ymin=80000, ymax=100000), color="red", fill="transparent", cex=3) +
  geom_rect(data=detect.sites[detect.sites$Label == "Chase",], aes(xmin=400000, xmax=410000, ymin=300000, ymax=310000), color="red", fill="transparent", cex=3) +
  geom_rect(data=detect.sites[detect.sites$Label == "Kyngs",], aes(xmin=500000, xmax=560000, ymin=270000, ymax=330000), color="red", fill="transparent", cex=3) +
  geom_rect(data=detect.sites[detect.sites$Label == "Nar",], aes(xmin=560000, xmax=590000, ymin=300000, ymax=325000), color="red", fill="transparent", cex=3) +
  geom_rect(data=detect.sites[detect.sites$Label == "Thwai",], aes(xmin=470000, xmax=540000, ymin=410000, ymax=450000), color="red", fill="transparent", cex=3) +
  geom_rect(data=detect.sites[detect.sites$Label == "Upton",], aes(xmin=630000, xmax=660000, ymin=300000, ymax=320000), color="red", fill="transparent", cex=3) +
  geom_text(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y, label="2"), nudge_y=-50000, cex=12) +
  geom_text(data=detect.sites[detect.sites$Label == "Chase",], aes(X,Y, label="1"), nudge_x=-30000, cex=12) +
  geom_text(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X,Y, label="3"), nudge_y=-60000, cex=12) +
  geom_text(data=detect.sites[detect.sites$Label == "Nar",], aes(X,Y, label="4"), nudge_x=10000, nudge_y=-40000, cex=12) +
  geom_text(data=detect.sites[detect.sites$Label == "Thwai",], aes(X,Y, label="5"), nudge_x=70000, cex=12) +
  geom_text(data=detect.sites[detect.sites$Label == "Upton",], aes(X,Y, label="6"), nudge_x=50000, cex=12) +
  coord_fixed(1) +
  theme_void() +
  theme(plot.margin=unit(c(t=0, r=0.25, b=0.25, l=0), unit="cm")) +
  north(uk_map, symbol=12, location="bottomleft")

bo = ggplot(bo_map) +
  geom_polygon(data=bo_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=bo2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y), color="red", cex=10) +
  geom_label(data=detect.sites[detect.sites$Label == "Bourn",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=12) +
  geom_label(data=detect.sites[detect.sites$Label == "Bourn",], aes(x=391000, y=419000, label="2."), cex=12) +
  coord_fixed(ratio=1, xlim=c(390000,420000), ylim=c(80000,100000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0, r=0, b=0.25, l=0.25), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
#  blank() +
  ggsn::scalebar(location="bottomleft", x.min=390000, x.max=400000, y.min=81000, y.max=85000, dist=5000, dist_unit="m", st.dist=0.2, height=0.2, transform=F)

ch = ggplot(ch_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=ch.sites, aes(X, Y), color="red", cex=10) +
  geom_text(data=ch.sites, aes(X, Y, label=Title), nudge_x=25, nudge_y=-60, cex=12) +
  geom_label(data=detect.sites[detect.sites$Label == "Chase",], aes(X, Y, label=Description), cex=10) +
  geom_label(data=detect.sites[detect.sites$Label == "Chase",], aes(x=403000, y=308800, label="1."), cex=10) +
  coord_fixed(ratio=1, xlim=c(402500,404100), ylim=c(307000,308900)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0, r=0.25, b=0.25, l=0.25), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
#  blank() +
  ggsn::scalebar(location="bottomleft", x.min=402500, x.max=403600, y.min=307010, y.max=307020, dist=300, dist_unit="m", st.dist=5, height=5, transform=F)
  
ky = ggplot(ky_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=na_map, aes(long,lat, group=group), fill="grey90", color="black") +
  geom_rect(aes(xmin=500000, xmax=525000, ymin=267000, ymax=273000), color="white", fill="white") +
  geom_point(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X, Y), color="red", cex=10) +
  geom_label(data=detect.sites[detect.sites$Label == "Kyngs",], aes(X, Y, label=Description), nudge_y=-3000, cex=12) +
  geom_label(data=detect.sites[detect.sites$Label == "Kyngs",], aes(x=501000, y=329000, label="3."), cex=12) +
  coord_fixed(ratio=1, xlim=c(500000,560000), ylim=c(270000,330000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0.25, r=0.25, b=0.25, l=0), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
#  blank() +
  ggsn::scalebar(location="bottomleft", x.min=500000, x.max=510000, y.min=270000, y.max=271000, dist=10000, dist_unit="m", st.dist=2, height=1, transform=F)

na = ggplot(na_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_point(data=detect.sites[detect.sites$Label == "Nar",], aes(X, Y), color="red", cex=10) +
  geom_label(data=detect.sites[detect.sites$Label == "Nar",], aes(X, Y, label=Description), nudge_x=0, nudge_y=2000, cex=12) +
  geom_label(data=detect.sites[detect.sites$Label == "Nar",], aes(x=561000, y=324000, label="4."), cex=12) +
  geom_rect(aes(xmin=559500, xmax=572200, ymin=299000, ymax=301500), color="white", fill="white") +
  coord_fixed(ratio=1, xlim=c(560000,590000), ylim=c(300000,325000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0.25, r=0.25, b=0.25, l=0.25), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
#  blank() +
  ggsn::scalebar(location="bottomleft", x.min=560000, x.max=565000, y.min=300100, y.max=301000, dist=5000, dist_unit="m", st.dist=1, height=1, transform=F)

th = ggplot(th_map) +
  geom_polygon(data=th_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=th2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=th3_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_rect(aes(xmin=470000, xmax=495000, ymin=405000, ymax=412000), fill="white", color="white") +
  geom_point(data=detect.sites[detect.sites$Label == "Thwai",], aes(X, Y), color="red", cex=10) +
  geom_label(data=detect.sites[detect.sites$Label == "Thwai",], aes(X, Y, label=Description), nudge_y=-2500, cex=12) +
  geom_label(data=detect.sites[detect.sites$Label == "Thwai",], aes(x=471000,y=449000, label="5."), cex=12) +
  coord_fixed(ratio=1, xlim=c(470000,540000), ylim=c(410000,450000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0.25, r=0, b=0.25, l=0.25), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
#  blank() +
  ggsn::scalebar(location="bottomleft", x.min=471000, x.max=480000, y.min=410000, y.max=415000, dist=10000, dist_unit="m", st.dist=0.2, height=0.3, transform=F)

up = ggplot(up_map) +
  geom_polygon(aes(long,lat,group = group), fill="grey90", color="black") +
  geom_polygon(data=up2_map, aes(long,lat,group = group), fill="grey90", color="black") +
  geom_rect(aes(xmin=629000, xmax=635000, ymin=290000, ymax=301000), color="white", fill="white") +
  geom_point(data=detect.sites[detect.sites$Label == "Upton",], aes(X, Y), color="red", cex=10) +
  geom_label(data=detect.sites[detect.sites$Label == "Upton",], aes(X, Y, label=Description), nudge_x=0, nudge_y=1000, cex=12) +
  geom_label(data=detect.sites[detect.sites$Label == "Upton",], aes(x=631000, y=319000, label="6."), cex=12) +
  coord_fixed(ratio=1, xlim=c(630000,660000), ylim=c(300000,320000)) +
  theme_void() +
  theme(plot.margin=unit(c(t=0.25, r=0, b=0, l=0), unit="cm"), panel.border=element_rect(color="black", fill=NA, size=2)) +
#  blank() +
  ggsn::scalebar(location="bottomleft", x.min=630000, x.max=631000, y.min=300000, y.max=300100, dist=3000, dist_unit="m", st.dist=5, height=4, transform=F)
 
png("map/sampling_map.png", width=9000, height=9000, units="px", res=200)
plot_grid(uk, ch, bo, ky, na, th, up, ncol=3, nrow=3, label_size=25, label_fontfamily=1)
dev.off()
```

```{r log session info}
sink("log_session_map-creation.txt")
sessionInfo()
citation()
sink()
```

```{r packages citation}
sink("map-creation_packages_citations.txt")
for (p in pack.list){
 print(citation(p))
}
sink()
```

```{r end}
print("end")
```